---
title: "Chicago Data"
output: html_notebook
---

I registered my application here: https://data.cityofchicago.org/profile/Alex-Fedotov/pr3p-5psv/app_tokens

The tokens for my application are: 
1. App Token: 
2. Secret Token: 

The API console https://data.cityofchicago.org/console.html mentioned on https://www.cityofchicago.org/city/en/narr/foia/sample_code0.html - doesn't work.

What does work is:

1. You open the home page: https://data.cityofchicago.org/

2. Find the data set you need in the main pannel, let's say "Beach Weather Stations" - https://data.cityofchicago.org/Parks-Recreation/Beach-Weather-Stations-Automated-Sensors-2016-Humi/7edu-s3u7

3. Click "Export" (light blue) in the row of the buttons, select SODA API panel (closed, opens on click);

4. Copy-paste the URL from API endpoint field
https://data.cityofchicago.org/resource/77jv-5zb8.json

5. Click 'API docs' to get to the Socrata page where this particular API is described;
https://dev.socrata.com/foundry/data.cityofchicago.org/77jv-5zb8

6. Explanations of the SoQL queries is here: https://dev.socrata.com/docs/queries/

7. In particular, we want to filter one station - Foster
https://data.cityofchicago.org/resource/77jv-5zb8.json /on Socrata page;
https://data.cityofchicago.org/resource/7edu-s3u7.json /on Chicago site page
the parameter is: 'station_name'='Foster Weather Station'

8. https://data.cityofchicago.org/resource/7edu-s3u7.json?$where=station_name = "Foster Weather Station"

df <- read.socrata("https://data.cityofchicago.org/resource/7edu-s3u7.csv?where=station_name = "Foster Weather Station"", app_token = token)

```{r}
# Install RSocrata package if you still #haven't.
install.packages("RSocrata")
# Load the library
library("RSocrata")

token <- "QtHfmZRhGqDjOrUPZWe3NTh8s"
df <- read.socrata("https://data.cityofchicago.org/resource/7edu-s3u7.csv", app_token = token)

# all the accessible data from all the stations
```

If we need data from one station we need to use a $where row filter in the SoQL request

```{r}
durl <- "https://data.cityofchicago.org/resource/7edu-s3u7.csv?$where=station_name = \"Foster Weather Station\""
#make sure you've escaped the double quotes

token <- "QtHfmZRhGqDjOrUPZWe3NTh8s"
fodf <- read.socrata(durl, token)
# it is unclear why the commented out version doesn't work
# fodf <- read.socrata(durl, app_token = token)
```

library('plyr')
library('rnoaa')
options(noaakey = "NbgcGSTExtVsfjGNSVmUJxsYtRykAPLc")

then the ncdc* functions start working
